Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
para on mean-subtraction

We may evaluate automatic MT measures in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07labelleddepseval}
have evaluated their success by comparing the measure to human
judgments of fluency and adequacy.  In other work,
e.g. \newcite{snover06ter}, measures are evaluated by comparison to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we pursue both kinds of
evaluation.

\begin{itemize}
\item one challenge of metric-evaluation: underlying doc difficulty 
  \begin{itemize}
  \item describe mean-subtraction
  \end{itemize}
\end{itemize}

>>>>

We may evaluate automatic MT measures in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07labelleddepseval}
have evaluated their success by comparing the measure to human
judgments of fluency and adequacy.  In other work,
e.g. \cite{snover06ter}, measures are evaluated by comparison to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we explore both kinds of
evaluation.

\textbf{JGK: I think the next paragraph belongs elsewhere}
\begin{itemize}
\item \sout{one challenge of metric-evaluation: underlying doc difficulty }
  \begin{itemize}
  \item \sout{describe mean-subtraction}
  \end{itemize}
\end{itemize}
When considering a candidate measure $m$, reporting correlations of
$m$ with absolute HTER scores can conflate $m$'s power in identifying
which of two candidate translations is better with $m$'s (and HTER)'s
ability to distinguish which of two source documents is more difficult
to translate. To avoid this conflation, we consider the mean-removed
$m$ and HTER scores; this lowers the correlations but ensures that the
reported correlations are among differences in the translations rather
than among differences in the underlying document.
